Twenty years of dynamic occupancy modelling – what’s been done, and where to next?

### 2024-03-22 Manuscript/domReview.qmd
progress on intro
intro progress

@@

>>>>

Over the past few decades the dynamic occupancy model and its extensions have been used to address a broad range of research questions and objectives. Authors have assessed patterns and trends of occupancy for threatened species, tested specific hypotheses on the drivers of occupancy, and generated predictions of occupancy under future conditions. These models are well-suited to non-equilibrium situations such as recovering, declining, or invasives species, where assumptions of conventional species distribution models cannot be met.

Dynamic occupancy models have three fundamental assumptions; i) that sites are closed to changes in occupancy between primary sampling occasions, ii) that all heterogeneity in occupancy, occupancy dynamics, and detection is accounted for by covariates, and iii) that detections are independent from one another. Much has been discussed with respect to the first assumption, the closure assumption. Considerably less has been said regarding heterogeneity and the implications of inadequately modelling it.

@@

We present a comprehensive overview of how the dynamic occupancy model has been applied in its first two decades, with a look to the key questions which remain on how DOM can best be used to address ecological questions.
